An elaborate data set on human gait and the effect of mechanical perturbations

### 2014-12-09 paper.tex
Metadata description overhaul, closes #21.
- A shorter, more complete example meta file is included.
- Descriptions of every possible meta data item are included.
- meta data section is reorganized.

Each trial directory contains a meta data file in the YAML format. There are
three main headings: \verb+study+, \verb+subject+, and \verb+trial+.

The \verb+study+ section contains identifying information for the overall
study, an identification number, name, and description. This is the same for
all meta data files in the study.

The \verb+subject+ provides key value pairs of information about the subject in
that trial. Each subject has a unique identification number and basic
anthropomorphic data is included.

The \verb+trial+ section contains the unique information about the trial. Each
trial has a unique identification number.

An example meta data file is shown in Figure \ref{fig:example-meta-data} and
the following gives and explanation of the contents.

\begin{figure*}
  \small
  \begin{verbatim}
    study:
            id: 1
            name: Gait Control Identification
            description: Perturb the subject during walking and running.
    subject:
            id: 0
    trial:
            id: 58
            subject-id: 0
            datetime: 2014-03-28
            notes: >
                    This is an unloaded trial (no subject) 10 minute protocol that
                    perturbs the subject longitudinally. The treadmill reference
                    markers were not in place. We have the four custom made metal
                    feet placed under the four corners of the treadmill to prevent
                    pitch and sway movements. In addition, we also have the front
                    left and rear right feet that were installed by Motek. We also
                    have +/-3g analog accelerometers (ADXL330) affixed to the four
                    corners of the main frame of the treadmill and wired into the
                    NI box. The right handrail is removed.
            nominal-speed: 0.8
            nominal-speed-units: meters per second
            stationary-platform: True
            pitch: False
            sway: False
            hardware-settings:
                    high-performance: True
            analog-channel-map:
                    Channel1.Anlg: F1Y1
                    Channel2.Anlg: F1Y2
                    Channel3.Anlg: F1Y3
                    Channel4.Anlg: F1X1
                    Channel5.Anlg: F1X2
                    Channel6.Anlg: F1Z1
                    Channel7.Anlg: F2Y1
                    Channel8.Anlg: F2Y2
                    Channel9.Anlg: F2Y3
                    Channel10.Anlg: F2X1
                    Channel11.Anlg: F2X2
                    Channel12.Anlg: F2Z1
                    Channel61.Anlg: Front_Left_AccX
                    Channel62.Anlg: Front_Left_AccY
                    Channel63.Anlg: Front_Left_AccZ
                    Channel64.Anlg: Back_Left_AccX
                    Channel65.Anlg: Back_Left_AccY
                    Channel66.Anlg: Back_Left_AccZ
                    Channel67.Anlg: Front_Right_AccX
                    Channel68.Anlg: Front_Right_AccY
                    Channel69.Anlg: Front_Right_AccZ
                    Channel70.Anlg: Back_Right_AccX
                    Channel71.Anlg: Back_Right_AccY
                    Channel72.Anlg: Back_Right_AccZ
            events:
                    A: Force Plate Zeroing
                    B: Calibration Pose
                    C: First Normal Walking
                    D: Longitudinal Perturbation
                    E: Second Normal Walking
                    F: Unloaded End
            files:
                    mocap: mocap-058.txt
                    record: record-058.txt
                    meta: meta-058.yml
  \end{verbatim}
  \caption{An example meta data YAML file.}
  \label{fig:example-meta-data}
\end{figure*}

\begin{description}
  \item[analog-channel-map] A key value mapping of strings specifying the name
    of the signal emmitted from the analog channels of the NI USB XXX.
  \item[cortex-version] (string) Matches the version of Cortex used to record
    the trial.
  \item[datetime] (string) A date formatted string giving the date and/or time
    of the trial in the \verb|YYYY-MM-DD| format.
  \item[dflow-version] (string) Matches the version of D-Flow used to record
    the trial.
  \item[events] A key value map which prescribes names to the events recorded
    in the record file.
  \item[files] (list) A key value mapping of files associated with this trial
    where the key is the file type and the values are the path to the file
    relative to this meta file.
  \item[hardware-settings] There are tons of settings for the hardware in both
    D-Flow, Cortex, and the other software in the system. This contains any
    non-default settings.
    \begin{description}
      \item[high-performance] (boolean) Indicates whether the D-Flow high
        performance setting was on (True) or off (False).
    \end{description}
  \item[id] (integer) A unique three digit identifier for the trial. All of the
    file names and directories associated with this trial include this.
  \item[marker-map] A string key value map which contains names for the
    markers.
  \item[marker-set] (string) Indicates the HBM \cite{Bogert2013} marker
    set used during the trial, either full, lower, or NA.
  \item[nominal-speed] (float) The nominal or base speed during the trial.
  \item[nominal-speed-units] (string) The units of the nominal speed.
  \item[notes] {string} Notes about the trial.
  \item[pitch] (boolean) Indicates if the pitch degree of freedom was acutated
    during the trial.
  \item[stationary-platform] (boolean) Indicates whether the treadmill
      sway or pitch motion was actuated during the trial. If this flag is
      false, the measured ground reaction forces must be compensated for the
      inertial affects and be expressed the forces and moments in the motion
      capture reference frame.
  \item[subject-id] (integer) A number corresponding to the subject in the
    trial.
  \item[sway] (boolean) Indicates if the lateral (sway) degree of freedom was
    acutated during the trial.
\end{description}

>>>>

Each trial directory contains a meta data file in the YAML format named in the
following style \verb|meta-xxx.yml| where \verb|xxx| is the three digit trial
identification number. There are three main headings in the file: \verb+study+,
\verb+subject+, and \verb+trial+. An example meta data file is shown in Listing
\ref{lis:example-meta-data}.

The \verb+study+ section contains identifying information for the overall
study, an identification number, name, and description. This is the same for
all meta data files in the study. Details are given below:

\begin{description}
  \item[id] An integer specifying a unique identification number of the study.
  \item[name] A string giving the name of the study.
  \item[description] A string with a basic description of the study.
\end{description}

The \verb+subject+ provides key value pairs of information about the subject in
that trial. Each subject has a unique identification number along with basic
anthropomorphic data. The following details the possible meta data for the
subject:

\begin{description}
  \item[age] An integer age in years of the subject at the time of the trial.
  \item[ankle-width-left] A float specifying the width of the subjects left
    ankle.
  \item[ankle-width-right] A float specifying the width of the subjects right
    ankle.
  \item[ankle-width-units] A string giving the units of measurement of the
    ankle widths.
  \item[id] An unique identification integer for the subject.
  \item[gender] A string specifying the gender of the subject.
  \item[height] A float specifying the measured height of the subject (with
    shoes on) at the time of the trial.
  \item[height-units] A string giving the units of the height measurement.
  \item[knee-width-left] A float specifying the width of the subjects left
    knee.
  \item[knee-width-right] A float specifying the width of the subjects right
    knee.
  \item[knee-width-units] A string giving the units of measurement of the
    knee widths.
  \item[mass] A float specifying the self-reported mass of the subject.
  \item[mass-units] A string specifying the units of the mass measurement.
\end{description}

The \verb+trial+ section contains the information about the particular trial.
Each trial has a unique identification number along with a variety of other
information, detailed below:

\begin{description}
  \item[analog-channel-map] A mapping of the strings D-Flow assigns to signals
    emmitted from the analog channels of the NI USB-6255 to names the user
    desires.
  \item[cortex-version] The version of Cortex used to record the trial.
  \item[datetime]A date formatted string giving the date of the trial in the
    \verb|YYYY-MM-DD| format.
  \item[dflow-version] The version of D-Flow used to record the trial.
  \item[events] A key value map which prescribes names to the alphabetic events
    recorded in the record file.
  \item[files] A key value mapping of files associated with this trial
    where the key is the DFlow file type and the value is the path to the file
    relative to the meta file.
  \item[hardware-settings] There are tons of settings for the hardware in both
    D-Flow, Cortex, and the other software in the system. This contains any
    non-default settings.
    \begin{description}
      \item[high-performance] A boolean value indicatin whether the D-Flow high
        performance setting was on (True) or off (False).
    \end{description}
  \item[id] An unique three digit integer identifier for the trial. All of the
    file names and directories associated with this trial include this number.
  \item[marker-map] A key value map which maps marker names in the mocap file
    to the user's desired names for the markers.
  \item[marker-set] Indicates the HBM~\cite{Bogert2013} marker set used during
    the trial, either full, lower, or NA.
  \item[nominal-speed] A float representing the nominal desired treadmill speed
    during the trial.
  \item[nominal-speed-units] (string) The units of the nominal speed.
  \item[notes] Any notes about the trial.
  \item[pitch] A boolean that indicates if the treamdill pitch degree of
    freedom was acutated during the trial.
  \item[stationary-platform] A boolean that indicates whether the treadmill
      sway or pitch motion was actuated during the trial. If this flag is
      false, the measured ground reaction forces must be compensated for the
      inertial affects and be expressed in the motion capture reference frame.
  \item[subject-id] An integer corresponding to the subject in the trial.
  \item[sway] A boolean that indicates if the treadmill lateral (sway) degree
    of freedom was acutated during the trial.
\end{description}

\begin{listing*}
  \small
  \begin{minted}[gobble=4]{yaml}
    study:
       id: 1
       name: Gait Control Identification
       description: Perturb the subject during walking and running.
    subject:
       id: 8
       age: 20
       mass: 70.0
       mass-units: kilograms
       height: 1.572
       height-units: meters
       knee-width-left: 107.43
       knee-width-right: 107.41
       knee-width-units: millimeters
       ankle-width-left: 70.52
       ankle-width-right: 67.66
       ankle-width-units: millimeters
       gender: male
    trial:
       id: 58
       subject-id: 8
       datetime: 2014-03-28
       notes: >
           The subject did a somersault during this trial instead of following
           instructions to walk. Will have to use for another study.
       nominal-speed: 0.8
       nominal-speed-units: meters per second
       stationary-platform: True
       pitch: False
       sway: False
       hardware-settings:
           high-performance: True
       dflow-version: 3.16.1
       cortex-version: 3.1.1.1290
       marker-map:
           M1: LHEAD
           M2: THEAD
           M3: RHEAD
           M4: FHEAD
           M5: C7
       analog-channel-map:
           Channel1.Anlg: F1Y1
           Channel2.Anlg: F1Y2
           Channel3.Anlg: F1Y3
           Channel4.Anlg: F1X1
       events:
           A: Force Plate Zeroing
           B: Calibration Pose
           C: First Normal Walking
           D: Longitudinal Perturbation
           E: Second Normal Walking
           F: Unloaded End
       files:
           compensation: ../T057/mocap-057.txt
           mocap: mocap-058.txt
           record: record-058.txt
           meta: meta-058.yml
  \end{minted}
  \caption{A fictious example of a YAML formatted meta data file. All of the
    possible keys in the data set are shown.}
  \label{lis:example-meta-data}
\end{listing*}
